### 2015-11-11 CVPR16/supplementarymaterial.tex
clean up supp

\usepackage{verbatim}
\usepackage{bm}
\usepackage{microtype}
\usepackage{url}
\usepackage{multirow}
\usepackage{subcaption}
\usepackage{booktabs} % for better tables

@@

\begin{document}
\section{Computation of ellipsoid parameters}
How to compute the parameters of ellipsoid in the camera coordinate frame when center and dimensions of the ellipsoid are given in tracklet coordinate frame.
\label{sec:sigmacomputation}

@@

\section{Projection of ellipsoid to image}
\newcommand{\mubar}{\bar{\mu}_i}
The perspective projection of an ellipsoid in general is not an ellipsoid in
general. We approximate the projection of ellipsoid by projecting a slice
through the ellipsoid.

\subsection{Tangent planes method}
\newcommand{\nx}{\hat{n}_x}
We chose the slice as the plane passing through the four points that touch 
the tangent planes through the origin.
Let the normal to plane representing $\xmin$, $\xmax$ be $\nx = [\cot(\alpha),
0, 1]^\top$. The tangent point lies on the plane, ellipsoid and at
the tangent point the gradient of ellipsoid is parallel to the plane normal.
%
\begin{align}
  x^\top \nx = \nx^\top x &= 0\\
  (x-\muic)^\top\Sigmaicf(x-\muic) &= 1 \\
  2\Sigmaicf (x - \muic) &= \lambda \nx \enspace .
\end{align}%
%
Eliminating $x$ from the three equations we get,
%
\begin{align}
  \frac{ \lambda^2 }{ 4 } \nx^\top \Sigmaicfinv \nx &= 1\\
  \frac{ \lambda }{ 2 } \nx^\top \Sigmaicfinv \nx - \muic^\top \nx &= 0
\end{align}%
%
Solving for $\lambda$ we get $\lambda = \frac{ 2 \muic^\top \nx }{ \nx^\top \Sigmaicfinv \nx }$ or
%
\begin{align}
  \nx^\top \muic \muic^\top \nx &= \nx^\top \Sigmaicfinv \nx\\
  \nx^\top (\Sigmaicfinv - \muic \muic^\top) \nx &= 0
\end{align}%
%
Let $C := \Sigmaicfinv - \muic \muic^\top$ and the quadratic equation can be solved by
%
\begin{align}
  \cot(\alpha) &= \frac{ - C_{13} \pm \sqrt{ C^2_{13} - C_{11}C_{33} } }{ C_{11}  }
\end{align}%
%
Similarly for $\beta_y$

@@

\subsection{Projection of the ellipsoid slice}
\begin{align}
  \np^\top x = x^\top\np &= 1\\ 
  (x-\muic)^\top\Sigmaicf(x-\muic) &= 1 \enspace.
\end{align}
We rewrite $\muic = \muic\np^\top x$, and $1 = x^\top\np \np^\top x$
\begin{align}
  (x-\muic\np^\top x)^\top\Sigmaicf(x-\muic\np^\top x) &= x^\top\np \np^\top x \enspace,
\end{align}
which is equivalent to 
\begin{align}
  x^\top\left((I-\muic\np^\top)^\top\Sigmaicf(I-\muic\np^\top) - \np \np^\top\right)x &= 0\enspace.
\end{align}

@@

\section{Localization}
\subsection{Other Energies}
\subsubsection{Lane energy}
\label{sec:laneEnergy}
 The lanes are modeled as splines. Here we assume that the confidence in lane
 detection is decreases as the distance from the lane center increases.  The
 energy is given by the dot product between car orientation and tangent to the
 lane at that point.

\begin{align}
  \label{eq:laneOrientationEnergy}
  \Energy{lane} = 
  \sum_{m \in M_{\text{close}}}
  (1 - \ori{i}{t} \cdot \text{TAN}(L_{m}(k), \pos{i}{t}) )
\LaneUncertainty{\pos{i}{t}}
\end{align}
where $M_{\text{close}} = \{m : \text{DIST}(L_{m}(k), \pos{i}{t}) < d_{\text{thresh}}\} $ is
the set of nearby lanes close to the object by a certain distance threshold $d_{\text{thresh}}$ and 
\begin{align}
\LaneUncertainty{\pos{i}{t}} = 
  \frac{1}{1 + \exp(-q(w_{\text{road}} - \text{DIST}(L_{m}(k), \pos{i}{t})))}
\end{align}
for some constant $w_{\text{road}}$ that represents the width of the road.

\subsubsection{Transition probability}
Dynamics constraints should not only enforce smooth trajectories, but also the
holonomic constraints.  The following energy adds a penalty if the change in
position is not in direction of previous orientation.

@@

\subsubsection{Size Prior}

@@

\section{Inference method Comparison}

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{results/0009_contPtTracks_size_bboxOcc_yawTstepWiseInference_0000000061.png}
  \includegraphics[width=\columnwidth]{results/0009_lane_size_bboxOcc_yawTstepWiseInference_0000000061.png}
  \caption{Qualitative localization results}
  \label{fig:qualLocalizationResults}
\end{figure}

>>>>

\usepackage{verbatim}
\usepackage{bm}
\usepackage{microtype}
\usepackage{url}
\usepackage{multirow}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{booktabs} % for better tables

@@

\begin{document}
\section{Computation of Ellipsoids}
How to compute the parameters of ellipsoid in the camera coordinate frame when center and dimensions of the ellipsoid are given in tracklet coordinate frame.
\label{sec:sigmacomputation}

@@

\section{Projection of Ellipsoids to Image}
\newcommand{\mubar}{\bar{\mu}_i}
The perspective projection of an ellipsoid in general is not an ellipsoid in
general. We approximate the projection of ellipsoid by projecting a slice
through the ellipsoid.

\subsection{Tangent plane method}
\newcommand{\nx}{\hat{n}_x}
We chose the slice as the plane passing through the four points that touch 
the tangent planes through the origin.
Let the normal to plane representing $\xmin$, $\xmax$ be $\nx = [\cot(\alpha),
0, 1]^\top$. The tangent point lies on the plane, ellipsoid and at
the tangent point the gradient of ellipsoid is parallel to the plane normal.
%
\begin{align}
  x^\top \nx = \nx^\top x &= 0\\
  (x-\muic)^\top\Sigmaicf(x-\muic) &= 1 \\
  2\Sigmaicf (x - \muic) &= \lambda \nx \enspace .
\end{align}%
%
Eliminating $x$ from the three equations we get,
%
\begin{align}
  \frac{ \lambda^2 }{ 4 } \nx^\top \Sigmaicfinv \nx &= 1\\
  \frac{ \lambda }{ 2 } \nx^\top \Sigmaicfinv \nx - \muic^\top \nx &= 0
\end{align}%
%
Solving for $\lambda$ we get $\lambda = \frac{ 2 \muic^\top \nx }{ \nx^\top \Sigmaicfinv \nx }$ or
%
\begin{align}
  \nx^\top \muic \muic^\top \nx &= \nx^\top \Sigmaicfinv \nx\\
  \nx^\top (\Sigmaicfinv - \muic \muic^\top) \nx &= 0
\end{align}%
%
Let $C := \Sigmaicfinv - \muic \muic^\top$ and the quadratic equation can be solved by
%
\begin{align}
  \cot(\alpha) &= \frac{ - C_{13} \pm \sqrt{ C^2_{13} - C_{11}C_{33} } }{ C_{11}  }
\end{align}%
%
Similarly for $\beta_y$

@@

\begin{align}
  \np^\top x = x^\top\np &= 1\\ 
  (x-\muic)^\top\Sigmaicf(x-\muic) &= 1 \enspace.
\end{align}
We rewrite $\muic = \muic\np^\top x$, and $1 = x^\top\np \np^\top x$
\begin{align}
  (x-\muic\np^\top x)^\top\Sigmaicf(x-\muic\np^\top x) &= x^\top\np \np^\top x \enspace,
\end{align}
which is equivalent to 
\begin{align}
  x^\top\left((I-\muic\np^\top)^\top\Sigmaicf(I-\muic\np^\top) - \np \np^\top\right)x &= 0\enspace.
\end{align}

@@

\section{Other Energies for 3D Object Localization}

\begin{comment}
\subsubsection{Lane energy}
\label{sec:laneEnergy}
 The lanes are modeled as splines. Here we assume that the confidence in lane
 detection is decreases as the distance from the lane center increases.  The
 energy is given by the dot product between car orientation and tangent to the
 lane at that point.

\begin{align}
  \label{eq:laneOrientationEnergy}
  \Energy{lane} = 
  \sum_{m \in M_{\text{close}}}
  (1 - \ori{i}{t} \cdot \text{TAN}(L_{m}(k), \pos{i}{t}) )
\LaneUncertainty{\pos{i}{t}}
\end{align}
where $M_{\text{close}} = \{m : \text{DIST}(L_{m}(k), \pos{i}{t}) < d_{\text{thresh}}\} $ is
the set of nearby lanes close to the object by a certain distance threshold $d_{\text{thresh}}$ and 
\begin{align}
\LaneUncertainty{\pos{i}{t}} = 
  \frac{1}{1 + \exp(-q(w_{\text{road}} - \text{DIST}(L_{m}(k), \pos{i}{t})))}
\end{align}
for some constant $w_{\text{road}}$ that represents the width of the road.
\end{comment}

\subsection{Dynamic energy}
Dynamics constraints should not only enforce smooth trajectories, but also the
holonomic constraints.  The following energy adds a penalty if the change in
position is not in direction of previous orientation.

@@

\subsection{Size energy}

@@

\begin{comment}
\section{Inference method Comparison}

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{results/0009_contPtTracks_size_bboxOcc_yawTstepWiseInference_0000000061.png}
  \includegraphics[width=\columnwidth]{results/0009_lane_size_bboxOcc_yawTstepWiseInference_0000000061.png}
  \caption{Qualitative localization results}
  \label{fig:qualLocalizationResults}
\end{figure}
\end{comment}
